---
title: "Home Page"
author: "Mike Wessel"
date: "Update 09/07/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


## Background

Collaborative Site For Aquatic Preserve Water Quality and Seagrass Assessment
All materials on this site are considered DRAFT work products.
A map of the seagrass transect locations is provided below 

# [Site List](https://mikewessel.github.io/AP/docs/sites.pdf){target="_blank"}
The hyperlink above includes a list of seagrass transects along with descriptive data used to summarize attributes of the transect for data management purposes is provided below which can be downloaded for viewing and commenting: 

Other tabs on this site include:
  Descriptive Statistics, 
  Visualizations, and 
  Analytical Results


```{r setup}

library(tidyverse)
library(sf)
library(haven)
library(plotly)
library(leaflet)
library(here)
library(sp)
library(maptools)
```

# Interactive Map 
A Display of aquatic preserve seagrass transect locations and associated FDEP Waterbody Identifiers (WBIDs) is provided below. Hovering the cursor over the transect location provides the site name while hoverig over the polygon presents the FDEP Waterbody Identifier.





```{r package-options, include=TRUE}
knitr::opts_knit$set(message=FALSE,echo=FALSE)

setwd(here::here("./shapes"))

#IWR_wbid <- sf::read_sf(dsn = ".", layer = "WBID_Run61")%>%
#    filter(WBID %in% c("1983A1","1983A","1983B","1991B","2065A","2065B","2065C","2065D","2065E","2065F","2065G","2065H1","1991A","2056A","2056B","3240A","3240B","3258A1","3258I"))

#st_write(st_as_sf(IWR_wbid),"IWR_wbid.shp")

IWR_wbid<-st_read("IWR_wbid.shp",quiet=TRUE)

CHAP_tr <- sf::read_sf(dsn = ".", layer = "CHAP_SG_Stat21_Proj",quiet=TRUE)
EBAP_tr <- sf::read_sf(dsn = ".", layer = "EBAP_SG_Stat21_Proj",quiet=TRUE)

# assign crs
IWR_wbid <- st_transform(IWR_wbid, crs = 4326)
CHAP_tr <- st_transform(CHAP_tr , crs = 4326)
EBAP_tr <- st_transform(EBAP_tr, crs = 4326)


both<- spCbind(IWR_wbid, CHAP_tr)





# plot
leaflet::leaflet() %>%
  leaflet::addProviderTiles(providers$CartoDB.Voyager) %>%
  leaflet::addPolygons(color = "#222", weight = 2, opacity = 1, fillOpacity = 0,label = ~lapply(WBID, htmltools::htmlEscape), data = IWR_wbid ) %>%
  leaflet::addCircles(color = "green", label = ~lapply(Site, htmltools::htmlEscape),data = CHAP_tr)%>%
  leaflet::addCircles(color = "blue", label = ~lapply(Site, htmltools::htmlEscape),data = EBAP_tr)
```



